Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-07-27 referee_process/second_submission/referee_response.tex

\begin{myquotation}
This Letter reports results from a numerical study of thermal
convection in a compressible fluid at unity Prandtl number and a range
of initial stratification. The main result is the scaling of the
Nusselt number with the Rayleigh number, supplemented by some
observations such as characteristic changes in the transition between
subsonic and supersonic regimes.

This problem is highly challenging. Ideally, a numerical exploration
should be guided by some theoretical insights or practical
observations. The present paper appears to be ``purely'' numerical
without such guidance, albeit some comparison with the well-known
problem of incompressible Rayleigh--Bernard convection. Nevertheless,
the results are significant and should be published. While I do not
wholeheartedly recommend this paper to PRL, I would not object to its
acceptance.

Below is a minor comment that the authors may find useful.

Most parts of the paper is relatively well written, except in the
introduction. Here, there is room for improvement. The introductory
paragraph is virtually empty. I would cite a couple of papers for
"These prior studies" and be specific about both "important insight"
and known "fundamental properties". The final paragraph of the
introduction has failed to fulfill its mission. I would explicitly
state (at least) the most significant result of the paper in this
paragraph.
\end{myquotation}
We have clarified the structure of the introduction paragraph.  We included
citations to prior work at high Ma and set the context for the present study
of fundamental heat transport at both low and high Ma.
The
most important result of the paper is called out in the last paragraph of the
introduction.

### 2017-08-01 tex/nusselt_paper.tex
density fig updates
adds a table of run parameters to the paper.

%\documentclass[iop]{emulateapj}
\documentclass[aps, prfluids, onecolumn, notitlepage, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
%\usepackage[all]{hypcap}

@@

\begin{document}
%%%%% Create nice title and abstract
\author{Evan H. Anders}
\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
\author{Benjamin P. Brown}
\affiliation{Department of Astrophysical \& Planetary Sciences, University of Colorado -- Boulder}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO}
\title{Convective heat transport in stratified atmospheres at low and high Mach number}

@@

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{./figs/density_v_ra.png}
\caption{\label{fig:nrho_v_ra} 
Solid symbols show the density contrast measured
in density scale heights between the upper and lower boundary, 
$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
Empty symbols show 
$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
At low $\epsilon$ the evolved
$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
At high $\epsilon$,
the density stratification decreases.  Once the mean 
Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
boundary layers. Larger symbols represent 3D runs.}
\end{figure}

@@

@@

\bibliography{../biblio.bib}
\end{document}

>>>>

%\documentclass[iop]{emulateapj}
\documentclass[aps, prfluids, onecolumn, notitlepage, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
\usepackage{longtable}
%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
%\usepackage[all]{hypcap}

@@

\begin{document}
%%%%% Create nice title and abstract
\author{Evan H. Anders}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author{Benjamin P. Brown}
\affiliation{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affiliation{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\title{Convective heat transport in stratified atmospheres at low and high Mach number}

@@

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/density_v_ra.png}
\caption{\label{fig:nrho_v_ra} 
Solid symbols show the density contrast measured
in density scale heights between the upper and lower boundary, 
$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
Empty symbols show 
$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
At low $\epsilon$ the evolved
$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
At high $\epsilon$,
the density stratification decreases.  Once the mean 
Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
boundary layers. Larger symbols represent 3D runs.}
\end{figure}

@@

\bibliography{../biblio.bib}

\appendix
\section{Table of run parameters}
In table \ref{table:run_info}, we report both the input parameters ($\epsilon$, Ra$_t$, resolution)
and output values (evolved Nu, Re, Ma, $n_\rho$) shown in the figures throughout this paper.
Simulation input values are listed in the first six columns.  The evolved Nusselt
number (Nu) is presented, as well as how far away the atmospheric maximum and minimum are from
the mean.  The Reynolds number (Re) at the midplane is reported.  The Mach number (Ma) is reported
in the same format as Nu.  The evolved number of density scale heights is reported, using the two
measurements described in Fig. \ref{fig:nrho_v_ra}.

%\begin{table}
\begin{center}
\begin{longtable}{ p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1cm} p{1.75cm} p{1.5cm} p{2.75cm} p{1cm} p{1.2cm}  }
\caption{Input and output values of simulations.\label{table:run_info}}\\
\hline
$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
\hline\hline \endfirsthead																													\\
\multicolumn{11}{c}%
{ \tablename\ \thetable{} -- continued from previous page} \\
\hline
$\epsilon$	&	Ra$_t$	&	3D	&	$n_z$	&	$n_x$	&	$n_y$	&	Nu					&	Re	&	Ma					&	$n_{\rho, \text{max}}$	&	$n_{\rho, \text{bounds}}$	\\
\hline \hline \endhead
\hline \endfoot
\hline \endlastfoot

\vspace{0.08cm}1	&	31.6	&	No	&	128	&	1024	&	---	&$	2.93	_{-	0.04	}^{+	0.00	}$&	7.96	&$	0.29	_{-	0.12	}^{+	2.10	}$&	2.12	&	2.11	\\
\vspace{0.08cm}1	&	46.4	&	No	&	128	&	1024	&	---	&$	3.45	_{-	0.00	}^{+	0.00	}$&	10.77	&$	0.32	_{-	0.14	}^{+	2.30	}$&	2.05	&	2.02	\\
\vspace{0.08cm}1	&	68.1	&	No	&	128	&	1024	&	---	&$	4.02	_{-	0.00	}^{+	0.00	}$&	14.20	&$	0.34	_{-	0.15	}^{+	2.51	}$&	1.95	&	1.91	\\
\vspace{0.08cm}1	&	100	&	No	&	128	&	1024	&	---	&$	4.67	_{-	0.00	}^{+	0.00	}$&	18.50	&$	0.37	_{-	0.16	}^{+	2.71	}$&	1.83	&	1.78	\\
\vspace{0.08cm}1	&	147	&	No	&	128	&	1024	&	---	&$	5.41	_{-	0.00	}^{+	0.00	}$&	23.90	&$	0.40	_{-	0.18	}^{+	2.94	}$&	1.71	&	1.64	\\
\vspace{0.08cm}1	&	215	&	No	&	128	&	1024	&	---	&$	6.27	_{-	0.00	}^{+	0.01	}$&	30.91	&$	0.43	_{-	0.19	}^{+	3.20	}$&	1.57	&	1.50	\\
\vspace{0.08cm}1	&	316	&	No	&	128	&	1024	&	---	&$	6.02	_{-	0.03	}^{+	0.06	}$&	33.82	&$	0.47	_{-	0.28	}^{+	4.63	}$&	1.36	&	1.30	\\
\vspace{0.08cm}1	&	464	&	No	&	128	&	1024	&	---	&$	6.84	_{-	0.02	}^{+	0.03	}$&	44.84	&$	0.52	_{-	0.34	}^{+	5.31	}$&	1.20	&	1.13	\\
\vspace{0.08cm}1	&	681	&	No	&	128	&	1024	&	---	&$	8.15	_{-	0.03	}^{+	0.06	}$&	62.50	&$	0.58	_{-	0.39	}^{+	5.85	}$&	1.00	&	0.91	\\
\vspace{0.08cm}1	&	1000	&	No	&	128	&	1024	&	---	&$	9.73	_{-	0.03	}^{+	0.06	}$&	87.05	&$	0.64	_{-	0.45	}^{+	6.45	}$&	0.93	&	0.68	\\
\vspace{0.08cm}1	&	1470	&	No	&	128	&	1024	&	---	&$	11.50	_{-	0.05	}^{+	0.09	}$&	118.63	&$	0.71	_{-	0.50	}^{+	7.07	}$&	0.95	&	0.45	\\
\vspace{0.08cm}1	&	2150	&	No	&	128	&	1024	&	---	&$	13.19	_{-	0.08	}^{+	0.11	}$&	156.07	&$	0.76	_{-	0.54	}^{+	7.51	}$&	0.98	&	0.27	\\
\vspace{0.08cm}1	&	3160	&	No	&	256	&	1024	&	---	&$	18.44	_{-	0.05	}^{+	0.17	}$&	220.66	&$	0.74	_{-	0.30	}^{+	5.01	}$&	1.28	&	0.08	\\
\vspace{0.08cm}1	&	4640	&	No	&	256	&	1024	&	---	&$	20.47	_{-	0.09	}^{+	0.33	}$&	276.37	&$	0.76	_{-	0.30	}^{+	5.03	}$&	1.39	&	-0.11	\\
\vspace{0.08cm}1	&	6810	&	No	&	256	&	1024	&	---	&$	16.27	_{-	0.11	}^{+	0.06	}$&	305.71	&$	0.83	_{-	0.59	}^{+	7.57	}$&	1.09	&	-0.07	\\
\vspace{0.08cm}1	&	$10^4$	&	No	&	256	&	1024	&	---	&$	20.43	_{-	0.21	}^{+	0.24	}$&	397.69	&$	0.79	_{-	0.35	}^{+	5.49	}$&	1.26	&	-0.21	\\
\vspace{0.08cm}1	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	16.10	_{-	0.99	}^{+	0.15	}$&	176.84	&$	0.39	_{-	0.13	}^{+	3.78	}$&	1.24	&	0.41	\\
\vspace{0.08cm}1	&	$10^{4.167}$	&	No	&	256	&	1024	&	---	&$	21.68	_{-	0.25	}^{+	0.26	}$&	497.30	&$	0.79	_{-	0.35	}^{+	5.15	}$&	1.31	&	-0.22	\\
\vspace{0.08cm}1	&	$10^{4.33}$	&	No	&	256	&	1024	&	---	&$	18.76	_{-	0.09	}^{+	0.04	}$&	499.72	&$	0.77	_{-	0.52	}^{+	6.17	}$&	1.36	&	0.16	\\
\vspace{0.08cm}1	&	$10^{4.5}$	&	No	&	256	&	1024	&	---	&$	25.74	_{-	0.24	}^{+	0.40	}$&	756.44	&$	0.81	_{-	0.34	}^{+	4.92	}$&	1.46	&	-0.38	\\
\vspace{0.08cm}1	&	$10^{4.667}$	&	No	&	512	&	2048	&	---	&$	28.66	_{-	0.37	}^{+	0.34	}$&	925.71	&$	0.83	_{-	0.35	}^{+	4.92	}$&	1.57	&	-0.46	\\
\vspace{0.08cm}1	&	$10^{4.833}$	&	No	&	512	&	2048	&	---	&$	30.92	_{-	0.81	}^{+	0.83	}$&	1085.26	&$	0.81	_{-	0.35	}^{+	4.80	}$&	1.61	&	-0.46	\\
\vspace{0.08cm}1	&	$10^5$	&	No	&	512	&	2048	&	---	&$	33.60	_{-	0.41	}^{+	1.03	}$&	1356.44	&$	0.82	_{-	0.33	}^{+	4.51	}$&	1.72	&	-0.55	\\
\vspace{0.08cm}1	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	29.67	_{-	1.90	}^{+	0.44	}$&	562.40	&$	0.38	_{-	0.14	}^{+	3.71	}$&	1.67	&	-0.22	\\
\vspace{0.08cm}0.5	&	14.7	&	No	&	64	&	256	&	---	&$	1.44	_{-	0.00	}^{+	0.00	}$&	2.25	&$	0.08	_{-	0.04	}^{+	0.10	}$&	2.90	&	2.90	\\
\vspace{0.08cm}0.5	&	21.5	&	No	&	64	&	256	&	---	&$	2.12	_{-	0.01	}^{+	0.01	}$&	4.90	&$	0.15	_{-	0.07	}^{+	0.18	}$&	2.77	&	2.77	\\
\vspace{0.08cm}0.5	&	31.6	&	No	&	64	&	256	&	---	&$	2.64	_{-	0.00	}^{+	0.00	}$&	7.20	&$	0.17	_{-	0.08	}^{+	0.22	}$&	2.68	&	2.68	\\
\vspace{0.08cm}0.5	&	46.4	&	No	&	64	&	256	&	---	&$	3.09	_{-	0.00	}^{+	0.00	}$&	9.71	&$	0.19	_{-	0.09	}^{+	0.24	}$&	2.61	&	2.61	\\
\vspace{0.08cm}0.5	&	68.1	&	No	&	64	&	256	&	---	&$	3.38	_{-	0.01	}^{+	0.01	}$&	12.18	&$	0.21	_{-	0.10	}^{+	0.29	}$&	2.57	&	2.57	\\
\vspace{0.08cm}0.5	&	100	&	No	&	64	&	256	&	---	&$	3.72	_{-	0.01	}^{+	0.01	}$&	15.22	&$	0.22	_{-	0.11	}^{+	0.33	}$&	2.52	&	2.52	\\
\vspace{0.08cm}0.5	&	100	&	Yes	&	64	&	128	&	128	&$	3.42	_{-	0.11	}^{+	0.06	}$&	13.42	&$	0.21	_{-	0.08	}^{+	0.33	}$&	2.56	&	2.57	\\
\vspace{0.08cm}0.5	&	147	&	No	&	128	&	512	&	---	&$	4.68	_{-	0.01	}^{+	0.01	}$&	21.21	&$	0.24	_{-	0.12	}^{+	0.32	}$&	2.39	&	2.40	\\
\vspace{0.08cm}0.5	&	215	&	No	&	128	&	512	&	---	&$	5.38	_{-	0.01	}^{+	0.02	}$&	27.44	&$	0.26	_{-	0.13	}^{+	0.35	}$&	2.31	&	2.31	\\
\vspace{0.08cm}0.5	&	316	&	No	&	128	&	512	&	---	&$	5.91	_{-	0.01	}^{+	0.03	}$&	34.73	&$	0.28	_{-	0.14	}^{+	0.41	}$&	2.24	&	2.24	\\
\vspace{0.08cm}0.5	&	464	&	No	&	128	&	512	&	---	&$	6.78	_{-	0.01	}^{+	0.01	}$&	46.22	&$	0.31	_{-	0.15	}^{+	0.44	}$&	2.13	&	2.12	\\
\vspace{0.08cm}0.5	&	681	&	No	&	128	&	512	&	---	&$	7.26	_{-	0.02	}^{+	0.05	}$&	60.53	&$	0.34	_{-	0.20	}^{+	0.57	}$&	2.07	&	2.06	\\
\vspace{0.08cm}0.5	&	1000	&	No	&	128	&	512	&	---	&$	7.87	_{-	0.04	}^{+	0.09	}$&	83.02	&$	0.39	_{-	0.26	}^{+	0.71	}$&	1.98	&	1.96	\\
\vspace{0.08cm}0.5	&	1000	&	Yes	&	128	&	256	&	256	&$	6.83	_{-	0.25	}^{+	0.18	}$&	46.03	&$	0.23	_{-	0.08	}^{+	0.38	}$&	2.19	&	2.19	\\
\vspace{0.08cm}0.5	&	1470	&	No	&	128	&	512	&	---	&$	9.37	_{-	0.05	}^{+	0.11	}$&	122.78	&$	0.47	_{-	0.32	}^{+	0.89	}$&	1.81	&	1.78	\\
\vspace{0.08cm}0.5	&	2150	&	No	&	128	&	512	&	---	&$	10.47	_{-	0.08	}^{+	0.22	}$&	160.98	&$	0.52	_{-	0.37	}^{+	1.05	}$&	1.78	&	1.75	\\
\vspace{0.08cm}0.5	&	3160	&	No	&	128	&	512	&	---	&$	12.09	_{-	0.06	}^{+	0.11	}$&	216.11	&$	0.58	_{-	0.41	}^{+	1.17	}$&	1.68	&	1.64	\\
\vspace{0.08cm}0.5	&	4640	&	No	&	128	&	512	&	---	&$	14.67	_{-	0.21	}^{+	0.47	}$&	295.41	&$	0.65	_{-	0.47	}^{+	1.32	}$&	1.48	&	1.42	\\
\vspace{0.08cm}0.5	&	6810	&	No	&	128	&	512	&	---	&$	17.62	_{-	0.17	}^{+	0.36	}$&	395.01	&$	0.68	_{-	0.43	}^{+	1.22	}$&	1.45	&	1.18	\\
\vspace{0.08cm}0.5	&	$10^4$	&	No	&	128	&	512	&	---	&$	18.69	_{-	0.38	}^{+	0.63	}$&	487.35	&$	0.74	_{-	0.54	}^{+	1.50	}$&	1.51	&	1.24	\\
\vspace{0.08cm}0.5	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	12.89	_{-	0.62	}^{+	0.30	}$&	146.92	&$	0.23	_{-	0.08	}^{+	0.45	}$&	1.83	&	1.81	\\
\vspace{0.08cm}0.5	&	$10^{4.167}$	&	No	&	128	&	512	&	---	&$	20.18	_{-	0.17	}^{+	0.40	}$&	625.83	&$	0.78	_{-	0.57	}^{+	1.53	}$&	1.55	&	1.18	\\
\vspace{0.08cm}0.5	&	$10^{4.33}$	&	No	&	256	&	1024	&	---	&$	21.88	_{-	0.20	}^{+	0.66	}$&	784.29	&$	0.82	_{-	0.60	}^{+	1.61	}$&	1.64	&	1.18	\\
\vspace{0.08cm}0.5	&	$10^{4.5}$	&	No	&	256	&	1024	&	---	&$	23.35	_{-	0.43	}^{+	0.80	}$&	954.16	&$	0.83	_{-	0.61	}^{+	1.62	}$&	1.71	&	1.22	\\
\vspace{0.08cm}0.5	&	$10^{4.667}$	&	No	&	256	&	1024	&	---	&$	24.70	_{-	0.32	}^{+	0.83	}$&	1162.50	&$	0.84	_{-	0.62	}^{+	1.58	}$&	1.77	&	1.23	\\
\vspace{0.08cm}0.5	&	$10^{4.833}$	&	No	&	256	&	1024	&	---	&$	24.25	_{-	0.23	}^{+	0.53	}$&	1261.88	&$	0.75	_{-	0.53	}^{+	1.38	}$&	1.84	&	1.37	\\
\vspace{0.08cm}0.5	&	$10^5$	&	No	&	256	&	1024	&	---	&$	30.14	_{-	0.15	}^{+	0.39	}$&	1677.07	&$	0.71	_{-	0.34	}^{+	0.87	}$&	1.70	&	1.03	\\
\vspace{0.08cm}0.5	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	23.05	_{-	1.04	}^{+	1.41	}$&	429.63	&$	0.21	_{-	0.08	}^{+	0.43	}$&	1.95	&	1.59	\\
\vspace{0.08cm}0.5	&	$10^{5.167}$	&	No	&	256	&	1024	&	---	&$	32.83	_{-	0.21	}^{+	0.54	}$&	2030.80	&$	0.70	_{-	0.32	}^{+	0.80	}$&	1.73	&	1.01	\\
\vspace{0.08cm}0.5	&	$10^{5.33}$	&	No	&	256	&	1024	&	---	&$	35.24	_{-	0.48	}^{+	0.77	}$&	2461.71	&$	0.69	_{-	0.30	}^{+	0.73	}$&	1.77	&	1.00	\\
\vspace{0.08cm}0.5	&	$10^{5.5}$	&	No	&	256	&	1024	&	---	&$	37.69	_{-	0.36	}^{+	0.70	}$&	3019.49	&$	0.69	_{-	0.28	}^{+	0.68	}$&	1.81	&	1.01	\\
\vspace{0.08cm}0.5	&	$10^{5.667}$	&	No	&	256	&	1024	&	---	&$	41.09	_{-	0.54	}^{+	1.16	}$&	3685.02	&$	0.69	_{-	0.28	}^{+	0.67	}$&	1.84	&	0.99	\\
\vspace{0.08cm}0.5	&	$10^{5.833}$	&	No	&	384	&	1536	&	---	&$	44.62	_{-	1.22	}^{+	1.73	}$&	4448.83	&$	0.68	_{-	0.27	}^{+	0.65	}$&	1.87	&	1.00	\\
\vspace{0.08cm}0.5	&	$10^6$	&	No	&	512	&	2048	&	---	&$	45.86	_{-	1.90	}^{+	3.76	}$&	4943.73	&$	0.64	_{-	0.24	}^{+	0.62	}$&	1.95	&	1.11	\\
\vspace{0.08cm}0.5	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	40.53	_{-	0.72	}^{+	0.66	}$&	1291.61	&$	0.20	_{-	0.08	}^{+	0.46	}$&	2.15	&	1.47	\\
\vspace{0.08cm}0.5	&	$10^{6.167}$	&	No	&	512	&	2048	&	---	&$	50.49	_{-	0.57	}^{+	1.42	}$&	6530.03	&$	0.69	_{-	0.26	}^{+	0.61	}$&	1.93	&	1.03	\\
\vspace{0.08cm}0.5	&	$10^{6.33}$	&	No	&	512	&	2048	&	---	&$	52.19	_{-	1.93	}^{+	3.12	}$&	6898.73	&$	0.60	_{-	0.16	}^{+	0.47	}$&	2.04	&	1.16	\\
\vspace{0.08cm}0.5	&	$10^{6.5}$	&	No	&	512	&	2048	&	---	&$	58.67	_{-	1.47	}^{+	1.93	}$&	9108.92	&$	0.65	_{-	0.22	}^{+	0.53	}$&	2.02	&	1.07	\\
\vspace{0.08cm}0.5	&	$10^{6.667}$	&	No	&	512	&	2048	&	---	&$	60.07	_{-	3.84	}^{+	7.15	}$&	10135.36	&$	0.59	_{-	0.14	}^{+	0.41	}$&	2.08	&	1.15	\\
\vspace{0.08cm}0.5	&	$10^{6.833}$	&	No	&	768	&	3072	&	---	&$	66.38	_{-	6.25	}^{+	12.74	}$&	12181.75	&$	0.59	_{-	0.14	}^{+	0.39	}$&	2.12	&	1.18	\\
\vspace{0.08cm}0.5	&	$10^7$	&	No	&	768	&	3072	&	---	&$	69.11	_{-	8.11	}^{+	17.04	}$&	13771.71	&$	0.55	_{-	0.10	}^{+	0.32	}$&	2.17	&	1.21	\\
\vspace{0.08cm}0.5	&	$10^{7.333}$	&	No	&	1024	&	4096	&	---	&$	88.26	_{-	9.52	}^{+	17.15	}$&	21760.02	&$	0.59	_{-	0.13	}^{+	0.36	}$&	2.17	&	1.13	\\
\vspace{0.08cm}0.5	&	$10^{7.667}$	&	No	&	1024	&	4096	&	---	&$	133.62	_{-	15.48	}^{+	22.94	}$&	27996.91	&$	0.53	_{-	0.11	}^{+	0.25	}$&	2.27	&	1.22	\\
\vspace{0.08cm}$10^{-4}$	&	14.7	&	No	&	64	&	256	&	---	&$	1.22	_{-	0.00	}^{+	0.00	}$&	1.26	&$	6.25	_{-	2.86	}^{+	3.65}\cdot 10^{-4}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	21.5	&	No	&	64	&	256	&	---	&$	1.90	_{-	0.01	}^{+	0.01	}$&	3.96	&$	1.63	_{-	0.76	}^{+	0.98}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	31.6	&	No	&	64	&	256	&	---	&$	2.48	_{-	0.01	}^{+	0.01	}$&	6.29	&$	2.16	_{-	1.01	}^{+	1.32}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	46.4	&	No	&	64	&	256	&	---	&$	2.91	_{-	0.00	}^{+	0.00	}$&	8.47	&$	2.43	_{-	1.16	}^{+	1.52}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	68.1	&	No	&	64	&	256	&	---	&$	3.30	_{-	0.01	}^{+	0.01	}$&	10.88	&$	2.62	_{-	1.28	}^{+	1.71}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	100	&	No	&	64	&	256	&	---	&$	3.75	_{-	0.01	}^{+	0.01	}$&	13.93	&$	2.82	_{-	1.39	}^{+	1.91}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	100	&	Yes	&	64	&	128	&	128	&$	3.19	_{-	0.10	}^{+	0.06	}$&	11.48	&$	2.53	_{-	9.97	}^{+	1.93}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	147	&	No	&	128	&	512	&	---	&$	4.33	_{-	0.01	}^{+	0.03	}$&	17.92	&$	3.04	_{-	1.53	}^{+	2.08}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	215	&	No	&	128	&	512	&	---	&$	4.90	_{-	0.02	}^{+	0.04	}$&	22.61	&$	3.22	_{-	1.63	}^{+	2.26}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	316	&	No	&	128	&	512	&	---	&$	5.60	_{-	0.01	}^{+	0.04	}$&	28.92	&$	3.41	_{-	1.74	}^{+	2.36}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	464	&	No	&	128	&	512	&	---	&$	6.38	_{-	0.02	}^{+	0.06	}$&	37.10	&$	3.61	_{-	1.84	}^{+	2.44}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	681	&	No	&	128	&	512	&	---	&$	6.64	_{-	0.01	}^{+	0.01	}$&	46.60	&$	3.86	_{-	2.14	}^{+	3.18}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	1000	&	No	&	128	&	512	&	---	&$	7.97	_{-	0.07	}^{+	0.28	}$&	65.85	&$	4.51	_{-	2.66	}^{+	3.95}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	1000	&	Yes	&	128	&	256	&	256	&$	6.72	_{-	0.19	}^{+	0.57	}$&	38.32	&$	2.88	_{-	1.09	}^{+	2.55}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	1470	&	No	&	128	&	512	&	---	&$	9.46	_{-	0.10	}^{+	0.33	}$&	85.91	&$	4.68	_{-	2.43	}^{+	3.47}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	2150	&	No	&	128	&	512	&	---	&$	10.16	_{-	0.05	}^{+	0.12	}$&	121.67	&$	5.62	_{-	3.47	}^{+	5.23}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	3160	&	No	&	128	&	512	&	---	&$	10.48	_{-	0.06	}^{+	0.08	}$&	172.16	&$	6.87	_{-	4.96	}^{+	7.75}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	4640	&	No	&	128	&	512	&	---	&$	12.19	_{-	0.10	}^{+	0.22	}$&	232.13	&$	7.88	_{-	5.91	}^{+	9.5}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	6810	&	No	&	128	&	512	&	---	&$	14.63	_{-	0.11	}^{+	0.20	}$&	323.63	&$	8.78	_{-	6.43	}^{+	9.88}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	No	&	128	&	512	&	---	&$	15.21	_{-	0.14	}^{+	0.32	}$&	391.38	&$	9.30	_{-	7.11	}^{+	11.7}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^4$	&	Yes	&	128	&	256	&	256	&$	11.92	_{-	0.40	}^{+	1.34	}$&	115.06	&$	2.85	_{-	1.13	}^{+	3.11}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{4.167}$	&	No	&	192	&	768	&	---	&$	17.46	_{-	0.56	}^{+	1.30	}$&	509.77	&$	9.86	_{-	7.49	}^{+	12.1}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{4.33}$	&	No	&	192	&	768	&	---	&$	16.05	_{-	0.06	}^{+	0.03	}$&	606.29	&$	1.02	_{-	0.80	}^{+	1.35}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{4.5}$	&	No	&	192	&	768	&	---	&$	20.03	_{-	0.39	}^{+	0.91	}$&	828.29	&$	1.15	_{-	0.89	}^{+	1.52}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{4.667}$	&	No	&	192	&	768	&	---	&$	24.33	_{-	0.53	}^{+	0.96	}$&	1120.39	&$	1.31	_{-	1.02	}^{+	1.79}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{4.833}$	&	No	&	256	&	1024	&	---	&$	23.33	_{-	0.45	}^{+	0.55	}$&	1314.40	&$	1.34	_{-	1.05	}^{+	1.97}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	No	&	256	&	1024	&	---	&$	27.83	_{-	0.47	}^{+	0.42	}$&	1766.70	&$	1.50	_{-	1.17	}^{+	2.19}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^5$	&	Yes	&	256	&	512	&	512	&$	21.11	_{-	1.69	}^{+	4.74	}$&	319.84	&$	2.46	_{-	1.07	}^{+	2.90}\cdot 10^{-3}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{5.167}$	&	No	&	256	&	1024	&	---	&$	36.38	_{-	1.85	}^{+	2.94	}$&	2427.10	&$	1.72	_{-	1.36	}^{+	2.58}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{5.33}$	&	No	&	256	&	1024	&	---	&$	38.93	_{-	2.43	}^{+	4.36	}$&	2987.80	&$	1.79	_{-	1.43	}^{+	2.73}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{5.5}$	&	No	&	256	&	1024	&	---	&$	44.63	_{-	3.00	}^{+	5.01	}$&	3935.62	&$	1.93	_{-	1.57	}^{+	2.94}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{5.667}$	&	No	&	384	&	1536	&	---	&$	42.89	_{-	5.99	}^{+	8.40	}$&	4340.88	&$	1.81	_{-	1.49	}^{+	2.86}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^{5.833}$	&	No	&	384	&	1536	&	---	&$	51.48	_{-	4.94	}^{+	8.45	}$&	6230.83	&$	2.25	_{-	1.89	}^{+	3.69}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	No	&	512	&	2048	&	---	&$	69.68	_{-	15.80	}^{+	28.24	}$&	7684.29	&$	2.10	_{-	1.74	}^{+	3.15}\cdot 10^{-2}	$&	3.00	&	3.00	\\
\vspace{0.08cm}$10^{-4}$	&	$10^6$	&	Yes	&	256	&	512	&	512	&$	38.50	_{-	4.71	}^{+	12.54	}$&	920.21	&$	2.26	_{-	1.02	}^{+	2.84}\cdot 10^{-3}	$&	3.00	&	3.00	\\
